Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-09 WSSSPE2_report/WSSSPE2_review.tex
adding author names to subsections in 7

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open source software, etc.
\item augment author lists to give credit to people who don’t now get credit (and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and data)
\item developing a well-defined standard for author contribution -- what level of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then using social media to bring more people into the review process than is traditional
\item determining where else software can be cited and recorded (e.g., acknowledgments sections of papers)
\item developing a taxonomy of contributors, tied to places that these metrics are already stored (e.g., ORCID)
\item making metadata more easy to add for software, creating incentive for providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of - simplify a way of measuring and documenting the overall credit given to an individual over different projects
\item thinking about publishing software vs journal - software does not have to be novel
\item determining guidelines for recommending software characteristics for tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

\subsubsection{First breakout discussion: Group B}
\note{writing in progress}

@@

\subsubsection{Remaining breakout discussions: Taxonomy of contributorship/guidelines for software for tenure review}
\note{writing to be done}

@@

\subsubsection{Remaining breakout discussions: Prizes}
\note{writing to be done}

>>>>

After this discussion, group A brainstormed about incentives,
with the following items suggested:
\begin{itemize}
\item running programming contests, creating bounties for contributing to open source software, etc.
\item augment author lists to give credit to people who don't now get credit (and making them machine readable)
\item developing a microcitation standard and mechanism (for both software and data)
\item developing a well-defined standard for author contribution -- what level of contribution rises to the level of authorship?
\item leveraging social media for citation and reviewing of content -- then using social media to bring more people into the review process than is traditional
\item determining where else software can be cited and recorded (e.g., acknowledgments sections of papers)
\item developing a taxonomy of contributors, tied to places that these metrics are already stored (e.g., ORCID)
\item making metadata more easy to add for software, creating incentive for providing software metadata -- note that this cannot be centralized
\item creating something like the h-index that tenure committees can make use of - simplify a way of measuring and documenting the overall credit given to an individual over different projects
\item thinking about publishing software vs journal - software does not have to be novel
\item determining guidelines for recommending software characteristics for tenure - perhaps draft guidelines then get ACM or IEEE agreement
\end{itemize}

\subsubsection{First breakout discussion: Group B}
\note{writing in progress by James Howison - expected 9 March 2015}

@@

\subsubsection{Remaining breakout discussions: Taxonomy of contributorship/guidelines for software for tenure review}
\note{writing in progress by Frank Seinstra - expected by 22 March 2015}

@@

\subsubsection{Remaining breakout discussions: Prizes}
\note{writing in progress by Suresh Marru - in a GitHub branch to be merged?}
